Linear regression for approximating real and synthetic data

### 2022-10-06 doc/paper/paper.tex
Paper stuff

We find that OLS creates a good fit for the Franke Function. We see few signs of overfitting, even for large polynomial degrees. This is most likely because the Franke function is a sum of exponents, which can be expanded into polynomials. We would expect to see higher polynomial degrees give us better and better prediction, when there is no noise that could give rise to overfitting. We find that our own implementation of OLS follows Scikit's implementation up to around polynomial degree DEGREE, at which point scikit's MSE diverges. We chalk this up to numerical errors and differing implementation of the normal equations, as we simply use the normal equation exactly, while scikit uses an implementation which is probably computationally more efficient but gives slight differences when comparing to the normal equation. See Fig. 1 for a comparison between the Franke function and our prediction, which shows that they are essentially identical. Fig. 2 shows the train and test MSE by polynomial degree, and shows that we are not overfitting even for polynomial degree 20.

However, when we introduce a stochastic noise, we see that overfitting happens rapidly. Without a regularization hyperparameter, we see that the parameters fluctuate wildly and our prediction suffers. Fig. 3 shows our prediction for polynomial degree, where we clearly see that we have overfit the model severly. See fig. NUMBER in the appendix for test MSE for more and more noisy target values.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix       %%% starting appendix
\section*{Appendix A: Head of First Appendix}
Avoid Appendices if possible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix B: Head of Second Appendix}
\subsection*{Subsection head in appendix}
The equation counter is not reset in an appendix and the numbers will
follow one continual sequence from the beginning of the article to the very end as shown in the following example.
\begin{equation}
a = b + c.
\end{equation}

>>>>

%%%%%%% FIGURES %%%%%%%%%
\begin{figure*} 
\centerline{\includegraphics[width=6.85in]{figure/frankenonoise.png}}
\caption{A comparison the our prediction and the Franke function with no noise}
\label{frankenonoise}
\end{figure*}

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/frankenonoisemse.png}}
\caption{Test and train MSE for the Franke function with no noise}
\label{frankenonoisemse}
\end{figure}

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/frankenonoiser2.png}}
\caption{Test and train R2-score for the Franke function with no noise}
\label{frankenonoiser2}
\end{figure}

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/frankenoisemse.png}}
\caption{Test and train MSE for the Franke function with noise}
\label{frankenoisemse}
\end{figure}

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/frankenoiser2.png}}
\caption{Test and train R2-score for the Franke function no noise}
\label{frankenoiser2}
\end{figure}

We find that OLS creates a good fit for the Franke Function. We see few signs of overfitting, even for large polynomial degrees. This is most likely because the Franke function is a sum of exponents, which can be expanded into polynomials. We would expect to see higher polynomial degrees give us better and better prediction, when there is no noise that could give rise to overfitting. See Fig.~\ref{frankenonoise} for a comparison between the Franke function and our prediction, which shows that they are essentially identical. Fig.~\ref{frankenonoisemse} and Fig.~\ref{frankenonoiser2} shows the train and test MSE and R2 by polynomial degree, and shows that we are not overfitting even for polynomial degree 25. The MSE for test in these plots is the average MSE for 100 bootstraps.

However, when we introduce a stochastic noise, we see that overfitting happens rapidly. Without a regularization hyperparameter, we see that the parameters fluctuate wildly and our prediction suffers. Fig.~\ref{frankenoisemse} and Fig.~\ref{frankenoiser2} shows our MSE and R2 up to polynomial degree 25, where we see that we are overfitting severely. See Fig.~\ref{frankienoisecomparison} in the appendix for test MSE for more and more noisy target values. Here we also see something a bit surprising: We see that our own implementation of OLS follows Scikit's implementation up to around polynomial degree DEGREE, at which point scikit's MSE increases rapidly. We chalk this up to numerical errors and differing implementation of the normal equations, as we simply use the normal equation exactly, while scikit uses an implementation which is probably computationally more efficient but gives slight differences when comparing to the normal equation. These differences seem to create a large error when the model is overfitted, which we can not adequately explain.

@@

As our model is not overfitting, we do not expect Ridge to offer much improvement.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix       %%% starting appendix
\section*{Appendix A: Plots}

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/frankienoisecomparison.png}}
\caption{Test and train MSE for the Franke function with no noise}
\label{frankienoisecomparison}
\end{figure}
